Append_smoothed_results

### 2016-11-07 Code/append_smoothed_results.Rmd

```{r save_specified_files}
save(dat.clean, dat2, BlackWhite, paired.ids, list.age.decomp.tables, list.cod.decomp.tables,
     file = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/main_datasets.Rdata")
```

>>>>

```{r save_specified_files}
save(dat.clean, dat2, BlackWhite, BlackWhiteSmooth, paired.ids, list.age.decomp.tables, list.cod.decomp.tables,
     file = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/main_datasets.Rdata")
```
